Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-31 W13report.tex
Sat spell check

The Figure \ref{fig-fpthresh} shows the 
effect of misestimating the noise in the detections for each of three different
seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
the number of additional false positives in an LSST size CCD given a fractional misestimation
of the noise in the image and a detection threshold (recall the baseline numbers are given in 
Table~\ref{tab-fp}).  A 1\% under-estimate of the noise
corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to
12 expected, and 1 additonal false positive in the worst seeing case, compared to 3 expected.  These numbers roughly
double if the noise is underestaimted by 2\%.
The bottom panels show 
the effect of over-estimating the noise in the measurement.  The effect is to reduce
the number of false positives.  A 1\% under-estimate of the noise typically results in 2 fewer false positives
per chip, at 5--sigma.

@@

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
background random Gaussian field.  We find that we can perform a 1--parameter correction to these curves that
yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
visit.  This correction involves scaling {\it down} the variance in the images by 2.5\%, 1.5\% and 1\% for 
v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our varaince estimates 
are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
which suggest that our variance planes {\it underestaimte} the true variance.  However, this makes clear that 
while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
efficiency.

@@

\item The empirical variance of the detection images in prefiltering
  and postfiltering are similar to within $1\%$
  (Table~\ref{tab-variance2}).  However, the propogated variance in the
  postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
  leading to a larger number of false positives when using the
  variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).

@@

\item The measured false detection rate is seen to scale with detection
  threshold in a manner consistent with theory (Figure~\ref{fig-fp_v_thresh}).
  A 1--parameter correction to the variance by 1--2.5\% brings these relationships
  into almost exact correspndence.  Optimization of the false detection vs. true source
  detection efficiency will require an understanding of the variance at the 1\% level.

@@

\item The kernel it able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
  without a catastrohic increase in the number of false positives.

@@

\item Higher order measuremnts on filtered sources are not yet available,
  meaning feature--based classification of systematic false positives is not yet possible.

@@

\item Using the mean squared error of a control sample of {\tt KernelCandiates}
  appears to be a promising way to understand the degree of over/underfitting
  of the kernel model (Figure~\ref{fig-MSE_CONTROL}).  This may be a 
  feasible technique to optimize the pipeline on a per--sensor basis.

>>>>

The Figure \ref{fig-fpthresh} shows the 
effect of misestimating the noise in the detections for each of three different
seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
the number of additional false positives in an LSST size CCD given a fractional misestimation
of the noise in the image and a detection threshold (recall the baseline numbers are given in 
Table~\ref{tab-fp}).  A 1\% under-estimate of the noise
corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to
12 expected, and 1 additional false positive in the worst seeing case, compared to 3 expected.  These numbers roughly
double if the noise is underestimated by 2\%.
The bottom panels show 
the effect of over-estimating the noise in the measurement.  The effect is to reduce
the number of false positives.  A 1\% under-estimate of the noise typically results in 2 fewer false positives
per chip, at 5--sigma.

@@

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
background random Gaussian field.  We find that we can perform a 1--parameter correction to these curves that
yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
visit.  This correction involves scaling {\it down} the variance in the images by 2.5\%, 1.5\% and 1\% for 
v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
efficiency.

@@

\item The empirical variance of the detection images in prefiltering
  and postfiltering are similar to within $1\%$
  (Table~\ref{tab-variance2}).  However, the propagated variance in the
  postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
  leading to a larger number of false positives when using the
  variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).

@@

\item The measured false detection rate is seen to scale with detection
  threshold in a manner consistent with theory (Figure~\ref{fig-fp_v_thresh}).
  A 1--parameter correction to the variance by 1--2.5\% brings these relationships
  into almost exact correspondence.  Optimization of the false detection vs. true source
  detection efficiency will require an understanding of the variance at the 1\% level.

@@

\item The kernel it able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
  without a significant increase in the number of false positives.

@@

\item Higher order measurements on filtered sources are not yet available,
  meaning feature--based classification of systematic false positives is not yet possible.

@@

\item Using the mean squared error of a control sample of {\tt KernelCandidates}
  appears to be a promising way to understand the degree of over/underfitting
  of the kernel model (Figure~\ref{fig-MSE_CONTROL}).  This may be a 
  feasible technique to optimize the pipeline on a per--sensor basis.
